\cvsection{Employment History}

\begin{cventries}

  \cventry
    {R\&D Team Lead, Tech Manager}
    {airSlate, Inc.}
    {Kyiv, Ukraine}
    {Aug. 2021 - Dec. 2021}
    {
      \begin{cvitems}
        \item {Researching the impact of services design on user experience and product performance.}
        \item {Development of load tests using Scala and Gatling.}
        \item {Setting up periodic runs of load tests using Jenkins, monitoring and analytics of product performance using InfluxDB, Prometheus and Grafana.}
        \item {Development of experimental CI/CD tools, research in the field of new technologies.}
        \item {Product public API design.}
        \item {Product technical management.}
        \item {R\&D Team leadership.}
        \item {Internal reports and meetups.}
      \end{cvitems}
    }

  \cventry
    {Software Architect}
    {airSlate, Inc.}
    {Kyiv, Ukraine}
    {Jan. 2020 - Aug. 2021}
    {
      \begin{cvitems}
        \item {Design of new features and internal products on field of workflow automation.}
        \item {New features review and approvals.}
        \item {Built and deployed overall service infrastructure utilizing Docker container, GitHub Actions, and several AWS stack(Including EC2, ECS, Route 53, S3, CloudFront, RDS, ElastiCache, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
        \item {I have been management many tech leads.}
        \item {Internal reports and meetups.}
      \end{cvitems}
    }

  \cventry
    {Senior Software Engineer}
    {PDFfiller, Inc.}
    {Kyiv, Ukraine}
    {Now. 2015 - Jan. 2020}
    {
      \begin{cvitems}
        \item {Support PDFfiller.com and create new features and internal products.}
        \item {Implemented backend services and tools using C++, C, PHP, MySQL, DynamoDB, Elasticsearch, RabbitMQ.}
        \item {Product Dockerization, build service discovery using Consul, working with AWS stack, CI/CD design and implementation.}
        \item {Code review and interviews of new employees. }
        \item {Design and implementation monitoring and alerting tools based on ELK stack, InfluxDB, Slack and Grafana.}
        \item {Implemented internal Distributed File System (WebDAV like).}
        \item {Implemented a mass mailing service with analytics and statistics (Mailgun like).}
        \item {Implemented internal Chanos Engineering service to test the company's products and services.}
        \item {Internal reports and meetups.}
      \end{cvitems}
    }

  \cventry
    {Senior Software Engineer}
    {Genesis}
    {Kyiv, Ukraine}
    {Sep. 2014 - Nov. 2015}
    {
      \begin{cvitems}
        \item {Implemented a mass mailing service with analytics and statistics (Mailgun like).}
        \item {Implemented backend services and tools using PHP, C, XLST, MySQL.}
        \item {Internal reports and meetups.}
      \end{cvitems}
    }

  \cventry
    {Full Stack Software Engineer}
    {Self-Employment}
    {WWW}
    {Feb. 2009 - Aug. 2014}
    {
      \begin{cvitems}
        \item {I have done freelance work and been self-employed for 5 years here.}
        \item {Implemented projects for the National Association of Power Engineers of Russia, various businesses, E-Shops and freight carriers.}
        \item {Moderation Drupal Framework forum community and help newbies.}
        \item {Used stack: Linux, Apache, MySQL, PHP and JavaScript.}
      \end{cvitems}
    }

  \cventry
    {Software Engineer}
    {Art. Lebedev Studio}
    {Moscow, Russia}
    {Jan. 2008 - Dec. 2008}
    {
      \begin{cvitems}
        \item {Development new features for existing clients of the company.}
        \item {Used stack: PHP, XML, MySQL.}
      \end{cvitems}
    }

\end{cventries}
